Manuscript_Graphics

### 2019-07-18 R Files/Manuscript_Graphics.Rmd
Image updates

Pos_BMI <- PE_old %>% group_by(BMI_range) %>% summarise(n = n(), Positivity = mean(Positivity))
Pos_BMI$Positivity <- round(Pos_BMI$Positivity, 3)
Pos_BMI$BMI_range <- factor(Pos_BMI$BMI_range, levels = c("<25", "25-40", ">40"))
bar_PosBMI <- ggplot(Pos_BMI, aes(fill = BMI_range, x = BMI_range, y = Positivity, label = Positivity)) + 
                     ylim(0,0.25) +
                     geom_bar(position = "dodge", stat = "identity", width = 0.5) +
                     geom_text(size = 3, position = position_dodge(0.9), vjust = -1) +
                     scale_fill_manual(values = c("lightblue", "dodgerblue", "navyblue")) +
                     ylab("Pulmonary Embolism Positivity Rate") + 
                     xlab("BMI Group") +
                     labs(fill = "BMI Group") +
                     theme(legend.position = "none") + 
                     ggtitle("Pulmonary Embolism Positivity Rate by BMI")

@@

Pos_AgeGender <- PE_old %>% group_by(Age_range, Gender) %>% summarise(n = n(),
                                                                      Positivity = mean(Positivity))
Pos_AgeGender$Positivity <- round(Pos_AgeGender$Positivity, 3)
Pos_AgeGender$Age_range <- factor(Pos_AgeGender$Age_range, levels = c("<18", "18-35", ">35"))
bar_PosAgeGender <- ggplot(Pos_AgeGender, aes(fill = Gender, x = Age_range,
                                               y = Positivity, label = Positivity)) +
                     ylim(0,0.25) +
                     geom_bar(position = "dodge", stat = "identity") +
                     geom_text(size = 3, position = position_dodge(0.9), vjust = -1) +
                     scale_fill_manual(values = c("lightblue", "navyblue")) +
                     ylab("Pulmonary Embolism Positivity Rate") + 
                     xlab("Age Group") +
                     ggtitle("Pulmonary Embolism Positivity Rate by Age and Gender ")

@@

Pos_BMILocation <- PE_old %>% group_by(BMI_range, Location) %>% summarise(n = n(),
                                                                      Positivity = mean(Positivity))
Pos_BMILocation$Positivity <- round(Pos_BMILocation$Positivity, 3)
Pos_BMILocation$BMI_range <- factor(Pos_BMI$BMI_range, levels = c("<25", "25-40", ">40"))
bar_PosBMILocation <- ggplot(Pos_BMILocation, aes(fill = Location, x = BMI_range,
                                               y = Positivity, label = Positivity)) + 
                     ylim(0,0.25) +
                     geom_bar(position = "dodge", stat = "identity") +
                     geom_text(size = 3, position = position_dodge(0.9), vjust = -1) +
                     scale_fill_manual(values = c("lightblue", "dodgerblue", "mediumblue", "navyblue")) +
                     ylab("Pulmonary Embolism Positivity Rate") + 
                     xlab("BMI Group") +
                     ggtitle("Pulmonary Embolism Positivity Rate by BMI and Gender ")

@@

bar_PosLocationBMI <- ggplot(Pos_BMILocation, aes(fill = BMI_range, x = Location,
                                               y = Positivity, label = Positivity)) + 
                     ylim(0,0.25) +
                     geom_bar(position = "dodge", stat = "identity") +
                     geom_text(size = 3, position = position_dodge(0.9), vjust = -1) +
                     scale_fill_manual(values = c("lightblue", "dodgerblue", "mediumblue", "navyblue")) +
                     ylab("Pulmonary Embolism Positivity Rate") + 
                     xlab("BMI Group") +
                     labs(fill = "BMI Group") +
                     ggtitle("Pulmonary Embolism Positivity Rate by BMI and Gender ")

@@

## Line Plot of Model Predictions
location <- c("ED", "ED", "ED", "ICU", "ICU", "ICU", "IN", "IN", "IN", "OUT", "OUT", "OUT")
BMI <- rep(c("<25", "25-40", ">40"), 4)
mod_probs <- c(.082, .107, .091, .133, .171, .146, .107, .139, .118, .072, .094, .079)
probs <- data.frame(Location = location, bmi = BMI, probs = mod_probs, color = color)

@@

ggsave(filename = "Images/Line_PosPreds.jpeg", plot = line_PosPreds,
       width = 7, height = 5, device = "jpeg")
ggsave(filename = "Images/Line_Labels_PosPreds.jpeg", plot = line_labels_PosPreds,
       width = 7, height = 5, device = "jpeg")
```

>>>>

Pos_BMI <- PE_old %>% group_by(BMI_range) %>% summarise(n = n(), Positivity = mean(Positivity))
Pos_BMI$Positivity <- round(Pos_BMI$Positivity, 3)
Pos_BMI$Signif <- c("*", "", "*")
Pos_BMI$BMI_range <- factor(Pos_BMI$BMI_range, levels = c("<25", "25-40", ">40"))
bar_PosBMI <- ggplot(Pos_BMI, aes(fill = BMI_range, x = BMI_range, y = Positivity, label = Positivity)) + 
                     ylim(0,0.25) +
                     geom_bar(position = "dodge", stat = "identity", width = 0.5) +
                     geom_text(size = 3, position = position_dodge(0.9), vjust = -1) +
                     geom_text(aes(label = Signif), size = 5, position = position_dodge(0.9),
                               vjust = -1.5) +
                     scale_fill_manual(values = c("lightblue", "dodgerblue", "navyblue")) +
                     ylab("Pulmonary Embolism Positivity Rate") + 
                     xlab("BMI Group") +
                     labs(fill = "BMI Group") +
                     theme(legend.position = "none") + 
                     ggtitle("Pulmonary Embolism Positivity Rate by BMI")

@@

Pos_AgeGender <- PE_old %>% group_by(Age_range, Gender) %>% summarise(n = n(),
                                                                      Positivity = mean(Positivity))
Pos_AgeGender$Positivity <- round(Pos_AgeGender$Positivity, 3)
Pos_AgeGender$Signif <- c("","","","","*","*")
Pos_AgeGender$Age_range <- factor(Pos_AgeGender$Age_range, levels = c("<18", "18-35", ">35"))
bar_PosAgeGender <- ggplot(Pos_AgeGender, aes(fill = Gender, x = Age_range,
                                               y = Positivity, label = Positivity)) +
                     ylim(0,0.25) +
                     geom_bar(position = "dodge", stat = "identity") +
                     geom_text(size = 3, position = position_dodge(0.9), vjust = -1) +
                     geom_text(aes(label = Signif), size = 5, position = position_dodge(0.9),
                               vjust = -1.5) +
                     scale_fill_manual(values = c("lightblue", "navyblue")) +
                     ylab("Pulmonary Embolism Positivity Rate") + 
                     xlab("Age Group") +
                     ggtitle("Pulmonary Embolism Positivity Rate by Age and Gender ")

@@

Pos_BMILocation <- PE_old %>% group_by(BMI_range, Location) %>% summarise(n = n(),
                                                                      Positivity = mean(Positivity))
Pos_BMILocation$Positivity <- round(Pos_BMILocation$Positivity, 3)
Pos_BMILocation$BMI_range <- factor(Pos_BMI$BMI_range, levels = c("<25", "25-40", ">40"))
bar_PosBMILocation <- ggplot(Pos_BMILocation, aes(fill = Location, x = BMI_range,
                                               y = Positivity, label = Positivity)) + 
                     ylim(0,0.25) +
                     geom_bar(position = "dodge", stat = "identity") +
                     geom_text(size = 3, position = position_dodge(0.9), vjust = -1) +
                     scale_fill_manual(values = c("lightblue", "dodgerblue", "mediumblue", "navyblue")) +
                     ylab("Pulmonary Embolism Positivity Rate") + 
                     xlab("BMI Group") +
                     ggtitle("Pulmonary Embolism Positivity Rate by BMI and Location")

@@

bar_PosLocationBMI <- ggplot(Pos_BMILocation, aes(fill = BMI_range, x = Location,
                                               y = Positivity, label = Positivity)) + 
                     ylim(0,0.25) +
                     geom_bar(position = "dodge", stat = "identity") +
                     geom_text(size = 3, position = position_dodge(0.9), vjust = -1) +
                     scale_fill_manual(values = c("lightblue", "dodgerblue", "mediumblue", "navyblue")) +
                     ylab("Pulmonary Embolism Positivity Rate") + 
                     xlab("BMI Group") +
                     labs(fill = "BMI Group") +
                     ggtitle("Pulmonary Embolism Positivity Rate by BMI and Location")

@@

## Line Plot of Model Predictions
location <- c("ED", "ED", "ED", "ICU", "ICU", "ICU", "IN", "IN", "IN", "OUT", "OUT", "OUT")
BMI <- rep(c("<25", "25-40", ">40"), 4)
mod_probs <- c(.082, .107, .091, .133, .171, .146, .107, .139, .118, .072, .094, .079)
probs <- data.frame(Location = location, bmi = BMI, probs = mod_probs)
probs$bmi <- factor(probs$bmi, levels = c("<25", "25-40", ">40"))

@@

ggsave(filename = "Images/Line_PosPreds.jpeg", plot = line_PosPreds,
       width = 7, height = 5, device = "jpeg")
ggsave(filename = "Images/Line_Labels_PosPreds.jpeg", plot = line_labels_PosPreds,
       width = 7, height = 5, device = "jpeg")

Pos_Loc <- PE_old %>% group_by(Location) %>% summarise(n = n(), Positivity = mean(Positivity))
Pos_Loc$Positivity <- round(Pos_Loc$Positivity, 3)
Pos_Loc$Signif1 <- c("*", "**", "*", "**")
Pos_Loc$Signif2 <- c("***", "***", "", "")
bar_PosLoc <- ggplot(Pos_Loc, aes(fill = Location, x = Location, y = Positivity, label = Positivity)) +
                     ylim(0,0.25) +
                     geom_bar(position = "dodge", stat = "identity", width = 0.5) +
                     geom_text(size = 3, position = position_dodge(0.9), vjust = -1) +
                     geom_text(aes(label = Signif1), size = 5, position = position_dodge(0.9), 
                               vjust = -1.5) +
                     geom_text(aes(label = Signif2), size = 5, position = position_dodge(0.9),
                               vjust = -2.5) +
                     scale_fill_manual(values = c("lightblue", "dodgerblue", "mediumblue" ,"navyblue")) +
                     ylab("Pulmonary Embolism Positivity Rate") + 
                     xlab("Location") +
                     labs(fill = "Location") +
                     theme(legend.position = "none") +
                     ggtitle("Pulmonary Embolism Positivity Rate by Location")

ggsave(filename = "Images/Bar_PosLocation.jpeg", plot = bar_PosLoc,
       width = 7, height = 5, device = "jpeg")

p1 <- .122; p2 <- .098; n1 <- 1097; n2 <- 1235
pp <- (p1*n1 + p2*n2) / (n1 + n2)
z <- (p1-p2)/(sqrt(pp*(1-pp)*(1/n1 + 1/n2)))
1-pnorm(z)
```

## Fix BMI graph
## Gender positivity (M = .122, F = .098)
## Gender X Age significance, add asterisks
--- 18-35 M v. 18-35 F p = .0295, no other significance
## BMI significance + p-value (chi-square), add asterisks
--- 25-40 higher than <25, p = .024
## Positivity by location, add asterisks, provide caption with p-values
--- ICU > OUT/ED p < .01, IN > ED p = .026
## Fix title of bmi + location
## Give caption for BMI scatterplot
